Details of specific functions

### 2018-10-12 inst/gitbook/03_specific-tutorials.Rmd
Minor changes in the gitbook

These models indicate support for a Trend model, and we can plot the relative support of all model AICc weights

@@

>>>>

These models indicate support for a Trend model, and we can plot the relative support of all model AICc weights.

@@

> Note that although AIC values are indicator of model best fit, it is also important to look at the parameters themselves.
For example OU can be really well supported but with an alpha parameter really close to 0, making it effectively a BM model [@Cooper2016].
